MassWateR: Improving quality control, analysis, and sharing of water quality data

### 2023-08-28 manu-draft.qmd
all png figs to svg or tif, additional formatting for PO

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "MassWateR: Improving Quality Control, Analysis, and Sharing of Water Quality Data"
bibliography: refs.bib
csl: plos-one.csl
author: 
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Benjamen Wetherill:
      email: bwetherill@acasak.com 
      institute: [ACA]
      correspondence: false
  - Jillian Carr:
      email: Jillian.Carr@umb.edu
      institute: [MASS]
      correspondence: false

institute:
  - TBEP: Tampa Bay Estuary Program, St. Petersburg, Florida 33701 USA
  - ACA: ACASAK Consulting, Boston, Massachusetts USA
  - MASS: Massachusetts Bays National Estuary Partnership, Boston, Massachusetts 02125 USA

@@

execute: 
  echo: false
  warning: false
  message: false
  ft.keepnext: false
  ft.align: left
  fig-dpi: 300
---

@@

@@

![Workflow demonstrating how a user could engage with the *MassWateR* package. WQX: Water Quality Exchange; QC: Quality Control.](images/workflow.png){#fig-workflow width=100% fig-alt="Workflow diagram showing four ways to engage with *MassWateR*"}

@@

![Pseudocode demonstrating the iterative process of importing a required data file for *MassWateR*.  All read functions import an Excel file from the user-specified path (e.g., `respth`) and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).](images/importflow.png){#fig-importflow fig-alt="Diagram showing pseudocode for importing and fixing a data file with *MassWateR*" width=100%}

@@

```{r}
#| echo: true
#| eval: false
qcMWRreview(fset = fsetls, output_dir = getwd())
```
```
#> Report created successfully! File located at /tmp/RtmpUzzrbC/qcreview.docx
```
![The first two of sixteen pages of the quality control report created by `qcMWRreview()` that evaluates the results data relative to data quality objectives.  The first page shows the data quality objectives for accuracy, frequency, and completeness.  The second page shows QC results for frequency and completeness.  Parameters shown in red or marked as 'MISS' failed the data quality objectives.  Users can edit the Word file as needed, e.g., entering the organization name or adding notes.
](images/qcex.png){#fig-qcex}

>>>>

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "MassWateR: Improving quality control, analysis, and sharing of water quality data"
bibliography: refs.bib
csl: plos-one.csl
crossref:
  fig-title: Fig
  fig-prefix: Fig 
author: 
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Benjamen Wetherill:
      email: bwetherill@acasak.com 
      institute: [ACA]
      correspondence: false
  - Jillian Carr:
      email: Jillian.Carr@umb.edu
      institute: [MASS]
      correspondence: false

institute:
  - TBEP: Tampa Bay Estuary Program, St. Petersburg, Florida, USA
  - ACA: ACASAK Consulting, Boston, Massachusetts USA
  - MASS: Massachusetts Bays National Estuary Partnership, Boston, Massachusetts, USA

@@

execute: 
  echo: false
  warning: false
  message: false
  ft.keepnext: false
  ft.align: left
  fig-format: svg
  fig-dpi: 300
---

@@

{{< pagebreak >}}

@@

![Workflow demonstrating how a user could engage with the *MassWateR* package. WQX: Water Quality Exchange; QC: Quality Control.](images/workflow.tif){#fig-workflow width=100% fig-alt="Workflow diagram showing four ways to engage with *MassWateR*"}

@@

![Pseudocode demonstrating the iterative process of importing a required data file for *MassWateR*.  All read functions import an Excel file from the user-specified path (e.g., `respth`) and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).](images/importflow.tif){#fig-importflow fig-alt="Diagram showing pseudocode for importing and fixing a data file with *MassWateR*" width=100%}

@@

```{r}
#| echo: true
#| eval: false
qcMWRreview(fset = fsetls, output_dir = getwd())
```
```
#> Report created successfully! File located at /tmp/RtmpUzzrbC/qcreview.docx
```
![The first two of sixteen pages of the quality control report created by `qcMWRreview()` that evaluates the results data relative to data quality objectives.  The first page shows the data quality objectives for accuracy, frequency, and completeness.  The second page shows QC results for frequency and completeness.  Parameters shown in red or marked as 'MISS' failed the data quality objectives.  Users can edit the Word file as needed, e.g., entering the organization name or adding notes.
](images/qcex.tif){#fig-qcex}
